Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-09 authorinstr_2.tex
niet veel

To achieve this a combination of (political) hashtags in combination with twitter activities is used. To know if a user mentions an account of an election candidate \cite{pol} semi-automatically scraped a number of these accounts. Furthermore they collected 181972 tweets about politics, before processing these tweets non-personal and spam accounts had to be filtered. 
\subsection{Tag based analysis}

@@

%TODO misschien wat meer info over het semantic web toevoegen.
After this process \cite{eventalign} uses multiple techniques to align a tweet with the respective event. The first technique used by \cite{eventalign} is Feature Extraction. Three featuresets are used:
\begin{itemize}
%TODO uitwerken
  \item Immediate Resource Leaves: TODO
  \item 1-Step Resource Leaves 
  \item DBPedia Concepts 
\end{itemize}
%TODO afmaken

>>>>

To achieve this a combination of (political) hashtags in combination with twitter activities is used. To know if a user mentions an account of an election candidate \cite{pol} semi-automatically scraped a number of these accounts. Furthermore they collected 181972 tweets about politics, before processing these tweets non-personal and spam accounts had to be filtered.

To classify the users a one vs all classifier is trained. (Which will recorgnize one party vs all other parties. 
\subsection{Tag based analysis}

@@

%TODO misschien wat meer info over het semantic web toevoegen.
After this process \cite{eventalign} uses multiple techniques to align a tweet with the respective event. The first technique used by \cite{eventalign} is Feature Extraction. Three featuresets are used:
\begin{itemize}
%TODO uitwerken
  \item Immediate Resource Leaves: Use only the URI which are most indicative of an event. This feature only uses literals and resources within the URI of an event. 
  \item 1-Step Resource Leaves: Use all literals and resources within 1 step from the URI of an event. 
  \item DBPedia Concepts: Also uses all the concepts from DBPedia 
\end{itemize}
%TODO afmaken
